The K2 Bright Star Survey

### 2019-05-06 paper/ms.tex
l-bfgs-b optimization code

This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.

>>>>

This is a classic linear convex optimization program with constraints, which we solve with the \texttt{scipy} \citep{scipy} L-BFGS-B nonlinear optimization code \citep{lbfgsb}. $\Lambda_{k,l}$ has analytic derivatives with respect to $w_j$ \citep[calculated with \texttt{autograd}][]{autograd}, and it is therefore extremely fast to optimize and converges well on a global solution.
